RBE/CS549 Project: Boat Tracking/Detection

### 2017-12-12 paper/main.tex
Add citation

For the underlying optical flow algorithm, we use Farneback's
[INSERT CITATION HERE] which is accessible in matlab as...

@@

\item[Jordan Burklund] Develop methods to segment and mask pixels that represent water. Explore methods using contours for object detection.
\end{description}
\end{document}

>>>>

For the underlying optical flow algorithm, we use Farneback's
\cite{farneback2003} which is accessible in matlab as
\texttt{opticalFlowFarneback}.

As an overview, the way that this optical flow algorithm works is to

@@

\item[Jordan Burklund] Develop methods to segment and mask pixels that represent water. Explore methods using contours for object detection.
\end{description}

\bibliographystyle{ieeetr}
\bibliography{cite}

\end{document}
